### 2017-10-03 ng-product.Rmd

---
layout: page
title: xwMOOC 딥러닝
subtitle: Structuring Machine Learning Projects
date: "`r Sys.Date()`"
output:
  html_document: 
    toc: yes
    keep_md: yes
  pdf_document:
    latex_engine: xelatex
mainfont: NanumGothic
---

```{r, include=FALSE}
source("tools/chunk-options.R")

knitr::opts_chunk$set(echo = TRUE, warning=FALSE, message=FALSE)

options(scipen = 999)
options(family="NanumGothic")
```

## 초모수 미세조정(Hyperparameter tuning)

## 정규화(Regularization)

## 최적화(Optimization)