### 2020-06-24 r-face-recognition.Rmd
start face image recognition

---
title: "딥러닝"
subtitle: "사람 얼굴 인식"
author:
  - name: "[Tidyverse Korea](https://www.facebook.com/groups/tidyverse/)"
    url: https://www.facebook.com/groups/tidyverse/
    affiliation: Tidyverse Korea
    affiliation_url: https://www.facebook.com/groups/tidyverse/
date: "`r Sys.Date()`"
output:
  html_document: 
    theme: journal
    toc: yes
    toc_depth: 2
    toc_float: true
    highlight: tango
    code_folding: show
    number_section: true
    self_contained: true
bibliography: bibliography.bib
csl: biomed-central.csl
urlcolor: blue
linkcolor: blue
editor_options: 
  chunk_output_type: console
---

``` {r, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, message=FALSE, warning=FALSE,
                      comment="", digits = 3, tidy = FALSE, prompt = FALSE, fig.align = 'center')
```

# 사람 얼굴인식 {#recognize-face}

```{r face-recognition}
devtools::install_github("bnosac/image",
                         subdir = "image.dlib",
                         build_vignettes = TRUE)

devtools::install_github("bnosac/image",
                         subdir = "image.libfacedetection",
                         build_vignettes = TRUE)

library(tidyverse)
library(magick)
library(image.libfacedetection)

```