### 2020-07-06 r-captcha.Rmd
added header and footer

---
title: "딥러닝"
subtitle: "캡챠(captcha)란?"
author:
  - name: "[Tidyverse Korea](https://www.facebook.com/groups/tidyverse/)"
    url: https://www.facebook.com/groups/tidyverse/
    affiliation: Tidyverse Korea
    affiliation_url: https://www.facebook.com/groups/tidyverse/
date: "`r Sys.Date()`"
output:
  html_document: 
    include:
      after_body: footer.html
      before_body: header.html
    theme: journal
    toc: yes
    toc_depth: 2
    toc_float: true
    highlight: tango
    code_folding: show
    number_section: true
    self_contained: true
bibliography: bibliography.bib
csl: biomed-central.csl
urlcolor: blue
linkcolor: blue
editor_options: 
  chunk_output_type: console
---

``` {r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, message=FALSE, warning=FALSE,
                      comment="", digits = 3, tidy = FALSE, prompt = FALSE, fig.align = 'center')

knitr::opts_knit$set(global.par = TRUE) 
```

# 테스트